%-------------------------
% Resume in LaTeX
% Author: Nikhil Badyal
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{03B1}{$\alpha$}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{0.5in}
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.nikhilbadyal.com/}{\Large Nikhil Badyal}} &  \href{mailto:possum-dawn-engulf@duck.com}{possum-dawn-engulf@duck.com} \\
  Remote, India & \href{https://github.com/nikhilbadyal}{github.com/nikhilbadyal} \\
  \href{https://www.nikhilbadyal.com/}{nikhilbadyal.com} & \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}\label{sec:summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Senior Software Engineer with 3+ years of experience}
    {Specialized in building scalable backend systems, multi-tenant SaaS architecture, and cloud infrastructure. Proven expertise in API development, ETL pipelines, DevOps, and Elasticsearch. Strong open source contributor with a focus on performance, reliability, and automation. Delivered solutions that improved system performance by \textbf{90\%} and reduced costs by \textbf{35\%}.}
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}\label{sec:education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Jadavpur University}{Kolkata, India}
    {Bachelor of Engineering in Computer Science and Engineering; GPA: 8.5}{July 2018 -- July 2022}
      \resumeItemListStart
        \resumeItem{Relevant Coursework}{Data Structures, Algorithms, Database Systems, Distributed Computing}
        \resumeItem{Honors}{Graduated with Distinction}
      \resumeItemListEnd
    \resumeSubheading
      {Jawahar Navodaya Vidyalaya}{JandK, India}
      {Senior Secondary; Percentage: 95\%}{Nov 2011 -- June 2018}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}\label{sec:experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Anchanto}{Remote, India}
    {Senior Software Engineer}{Feb 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Multi-Tenant Architecture Lead}
          {Led migration from single-tenant to multi-tenant SaaS platform, supporting \textbf{100+ customers}, achieving \textbf{~35\%} cost reduction and \textbf{50\%} reduced downtime.}
        \resumeItem{Tooling Development}
          {Created \textbf{EsXport}, an open-source Elasticsearch data extraction tool reducing export times by \textbf{90\%}.}
        \resumeItem{Feature Development}
          {Built whitelabeled branded URLs, enabling custom domains and boosting customer satisfaction by \textbf{20\%}.}
        \resumeItem{Centralized Logging System}
          {Implemented ELK-based logging pipeline handling \textbf{600GB+} daily logs, accelerating issue resolution by reducing MTTR by \textbf{40\%}.}
        \resumeItem{Team Leadership and Mentorship}
          {Mentored developers through sprint planning, code reviews, and architectural guidance, increasing productivity and software quality.}
      \resumeItemListEnd

    \resumeSubheading
    {Anchanto}{Remote, India}
    {Software Engineer}{May 2022 -- Feb 2024}
      \resumeItemListStart
        \resumeItem{API Development}
          {Optimized \textbf{50+} APIs handling \textbf{20M+} daily requests, managing \textbf{100M+} parcels and \textbf{5B+} events. Maintained \textbf{90\%+} test coverage.}
        \resumeItem{System Designer}
          {Designed efficient database schemas enabling real-time tracking and searches across millions of parcels.}
        \resumeItem{ETL Engineer}
          {Developed ETL pipelines handling \textbf{5B+} records from \textbf{100+} carriers, enhancing parcel tracking and integration efficiency.}
        \resumeItem{Cloud Infrastructure Engineer}
          {Managed cloud infrastructure, achieving \textbf{30\%} cost reduction and maintaining \textbf{99.99\%} SLA.}
        \resumeItem{Data Tooling Engineer}
          {Built \textbf{Esyncer}, a tool syncing SQL data to Elasticsearch for faster search capabilities.}
        \resumeItem{Performance Engineer}
          {Reduced query response from \textbf{30 sec} to \textbf{2 ms} by optimizing Elasticsearch integration and replication for \textbf{100M+} parcels.}
        \resumeItem{DevOps Engineer}
          {Dockerized infrastructure reducing setup time from days to hours, enhancing environment consistency and scalability.}
      \resumeItemListEnd

    \resumeSubheading
    {Anchanto}{Remote, India}
    {Software Engineering Intern}{Jan 2022 -- May 2022}
      \resumeItemListStart
        \resumeItem{Backend \& ETL Engineer}
          {Developed \textbf{10+} APIs, optimized data transformation scripts handling \textbf{10M} parcels and \textbf{100M} events.}
        \resumeItem{CI/CD Pipeline Automation}
          {Implemented automated CI/CD pipelines, reducing deployment from days to minutes and ensuring consistent, reliable deliveries.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------AWARDS AND RECOGNITION-----------------
\section{Awards and Recognition}\label{sec:awards-and-recognition}
  \resumeSubHeadingListStart
    \resumeSubItem{Anchanto Innovation Challenge Winner – Operational Efficiency (2024)}
      {Recognized for building a \textbf{low-code integration engine} that significantly accelerated the development of carrier integrations. By using JSON-based configurations to define data sources,
       processing rules, and destinations, we eliminated repetitive coding and achieved faster deployment cycles, improving integration time-to-market and operational scalability.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}\label{sec:projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Esxport}
      {Open-source Python tool to efficiently export Elasticsearch indices into CSV files, significantly reducing export time. \href{https://github.com/nikhilbadyal/esxport}{[GitHub]}}
    \resumeSubItem{PGExtras}
      {Unofficial Python port of Heroku's pgextras, providing detailed statistics and analytics for PostgreSQL instances. \href{https://github.com/nikhilbadyal/pgextras}{[GitHub]}}
    \resumeSubItem{Cloudflare Worker Analytics Tracker}
      {Serverless analytics logging system built using Cloudflare Workers, with advanced data sanitization, security features, and rate limiting. \href{https://github.com/nikhilbadyal/nikhilbadyal.github.io/tree/main/tracker}{[GitHub]}}
    \resumeSubItem{VαultSync}
      {Automated backup solution for Bitwarden vaults supporting multi-cloud storage, featuring a backend API (FastAPI) and intuitive web UI (React + Vite). \href{https://github.com/nikhilbadyal/bitwarden-backup}{[GitHub]}}
    \resumeSubItem{Release Tracker}
      {Multi-platform software release monitoring tool that tracks updates from GitHub, GitLab, PyPI, APKMirror, and more with smart notifications. \href{https://github.com/nikhilbadyal/release-tracker}{[GitHub]}}
    \resumeSubItem{Telegram Channel Scraper}
      {Python-based scraper that concurrently downloads and filters files from Telegram channels, integrated with Cloudflare R2 for scalable cloud storage. \href{https://github.com/nikhilbadyal/telegram-scrapper}{[GitHub]}}
    \resumeSubItem{Notion Backup}
      {Modular Python tool to automatically backup Notion workspaces with cloud integration and extensive notification support across 70+ services. \href{https://github.com/nikhilbadyal/notion-backup}{[GitHub]}}
    \resumeSubItem{Docker Py Revanced}
      {Simplified one-click Python utility for building Revanced Android applications using Docker. \href{https://github.com/nikhilbadyal/docker-py-revanced}{[GitHub]}}
    \resumeSubItem{KeepNotes}
      {Cross-platform note-taking app with a clean UI built using Flutter and Dart. \href{https://github.com/nikhilbadyal/keepnotes}{[GitHub]}}
    \resumeSubItem{Tg-TOTP}
      {Telegram bot for generating secure temporary 2FA tokens directly within chat. \href{https://github.com/nikhilbadyal/tg-totp}{[GitHub]}}
    \resumeSubItem{Capstone: Movie Review Sentiment Analyzer}
      {Built a scalable MLOps pipeline using MLflow for experiment tracking, DVC for data versioning, and FastAPI for real-time model serving. Ensured reproducibility and efficient deployment. \href{https://github.com/nikhilbadyal/capstone}{[GitHub]}}

  \resumeSubHeadingListEnd

%--------TECHNOLOGIES SUMMARY------------
\section{Technologies Summary}\label{sec:technologies-summary}
\begin{tabularx}{\textwidth}{X X}
    \textbf{Languages:} Python, C++, SQL, Dart & \textbf{Databases:} PostgreSQL, Redis, Elasticsearch \\
    \textbf{Frameworks:} Django, Flutter & \textbf{Cloud Platforms:} AWS (EC2, S3, RDS, IAM) \\
    \textbf{DevOps:} Docker, GitHub Actions, Git & \textbf{Infrastructure as Code:} AWS CloudFormation \\
    \textbf{MLOps:} MLflow, DVC & \textbf{Monitoring/Reverse Proxy:} ELK Stack, Nginx \\
    \textbf{Other Tools:} Cloudflare Workers, CI/CD Pipelines & \\
  \end{tabularx}

%-------------------------------------------
\end{document}
